---
title: "X-META Dynamic Report"
header-includes:
- \usepackage{titling}
- \usepackage{fancyhdr}
- \graphicspath{{/srv/shiny-server/0408/}}
- \pagestyle{fancy}
- \fancyhead[RE,RO]{\includegraphics[width=7cm]{CCEB.png}}
- \fancypagestyle{plain}{\pagestyle{fancy}}
output: pdf_document 
params:
  n: NA
---

# 1 Introduction
## 1.1 What is X-meta?
### X-meta is an open-sourced, well-documented and interactive toolbox for meta-analysis.There are three main components to this toolbox: An R package called "xmeta", video tutorials and documentation for the package and an online analysis platform. 
### Xmeta package offers several functions for performing meta-analysis and visualizing outcomes, allowing users to conduct robust multivariate meta-analysis (mmeta), publication bias test (PB), outcome reporting bias test (ORB) and novel visualization tool (galaxy). Through the tutorials, reference documents and sample code, users can have a comprehensive exploration of the features found in XMETA and how they may apply to analytical work. The online meta-analysis system works with different available methods and a variety of formats of data, enabling users to quickly obtain the meta-analysis results without writing any code. 
### Please check https://www.xmeta.wiki/ to explore more features. 

## 1.2 About the method and dataset
### According to the uploaded dataset, this is a report for _Univariate Meta-analysis_ with _Binary Outcomes_. 

## 1.3 In this meta-analysis report, you can get:
### 1. Your uploaded data <br />
### 2. Summary <br />
### 3. Forest Plot <br />
### 4. Sensitivity Analysis (Fixed & Random Effect Model) <br />
### 5. Funnel plot for Publication bias test <br />
\newpage

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(metasens)
library(metafor)
```

# 2 Dataset & Analysis
## 2.1 Here is the dataset you uploaded:
There are overall `r dim(params$n)[1]` studies in the dataset. 
\vspace{0.5cm}
```{r,echo=FALSE}
params$n
```
\vspace{1cm}



## 2.2 Summary:
\vspace{0.5cm}
```{r,echo=FALSE}
mb1 <- metabin(Ee, Ne, Ec, Nc, sm = "OR", method = "I", data = params$n,studlab =study)
mb1
```
\vspace{1cm}

## 2.3 Forest plot:
\vspace{0.5cm}
```{r,echo=FALSE,fig.pos= "hbtp",fig.height=8,fig.width=14}
forest(mb1)
```

## 2.4 Heterogeneity test statistics (you can also get these results from Summary):
The value of ${tau}^2$ is `r (mb1$tau)^2`; the value of $I^2$ is `r round((mb1$I2)*100,digit =2)`$\%$.

## 2.5 Sensitivity test:
\vspace{0.5cm}
```{r,echo=FALSE,fig.pos= "hbtp",fig.height=8,fig.width=14}
fix <- metacum(mb1, pooled = 'fixed')
forest(fix)
random <- metacum(mb1, pooled = 'random')
forest(random)
```


## 2.6 Publication bias test:
```{r,echo=FALSE,fig.height=10,fig.width=14,results='hide',warning=FALSE}
funnel <- funnel(mb1,level=0.95,contour=c(0.9, 0.95, 0.99), shade=c("darkgray", "gray", "lightgray"))
legend(-30, 1.25,c("0.1 > p > 0.05","0.05 > p > 0.01", "< 0.01"),fill=c("darkgray", "gray", "lightgray"),bty="n")
```


